### 2023-08-14 appendix.tex
up

@@

\section{More Appendix thing if necessary}\label{appendix brp VASS}

\begin{theorem*}{\textbf{\ref{brp VASS}}.}
{\sc $k$-resilience }  and {\sc Bounded resilience} in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ are decidable%, and moreover {\sc $k$-resilience } is in $\EXPSPACE$
.
\end{theorem*}

>>>>

\mathieu{Thinking about using reset-VAS to simplify notations.}

@@

\section{Resilience for VASS}\label{appendix brp VASS}

As mentionned in Section~\ref{section VASS}
{\sc $k$-resilience }  and {\sc Bounded resilience} in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ are decidable. This stems from the fact that there are simple conditions in VASS that ensure neither {\sc $k$-resilience }  nor {\sc Bounded resilience} hold.
Restricting oneself to the case where these conditions are not met simplifies the problem.

\begin{theorem*}{{\em \textbf{\ref{brp VASS}}}.}
{\sc $k$-resilience }  and {\sc Bounded resilience} in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ are decidable%, and moreover {\sc $k$-resilience } is in $\EXPSPACE$
.
\end{theorem*}
